---
title: "Linear Models"
output: github_document
---

```{r setup,message=FALSE}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```


# Model Fitting

## Import data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```


## Fit a model
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

fit the model we care about
```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

look at the results...
```{r, include = FALSE}
fit

summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
residuals(fit)
```

Let's look at the results better
```{r}
broom::glance(fit)

broom::tidy(fit) %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "borough", "Borough: ")) %>% 
  knitr::kable(digits = 3)
```


## Be in control of factors

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    #factor in order of frequency
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )
```

look at the plot again
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

broom::tidy(fit)
broom::glance(fit)
```


## Diagnostics

```{r}
#add a column related to the residuals
#value of comparing to the actual value
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  #exclude some outliers
  ylim(-500, 1500)

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) + 
  geom_point() + 
  facet_wrap(. ~ borough)
```


## Hypothesis tests

This does t-test by default:
```{r}
fit %>% 
  broom::tidy() 
```

What about the significance of 'borough':
```{r}
fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
  #results(p-value) show there is significance difference
```


## Nest data, fit models

This is pretty formal and complex
```{r}
fit = lm(price ~ stars * borough + room_type * borough, data = nyc_airbnb)

broom::tidy(fit)
```

This is more exploratory but maybe more easier to understand
```{r}
nyc_airbnb %>% 
  #nest data except borough
  nest(data = -borough) %>% 
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  #filter(term == "stars")
  #significant association between stars and price in Manhattan
  filter(term != "(Intercept)") %>% 
  select(borough, term, estimate) %>% 
  pivot_wider(
    names_from = borough,
    values_from = estimate
  )
```



Let's nest even more...
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) +
  geom_point() +
  facet_wrap(. ~ term) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```


## Logistic Regression

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  #prob of being a expensive airbnb based on stars and roomtype
  mutate(
    expensive_apt = as.numeric(price > 500)
  )
```

let's fit a logistic regression for the binary outcome
```{r}
logistic_fit = 
  glm(
    expensive_apt ~ stars + borough,
    data = nyc_airbnb,
    #default: simple linear
    family = binomial())

logistic_fit %>% 
  broom::tidy() %>% 
  #more tidy
  mutate(
    term = str_replace(term, "borough", "Borough: "),
    estimate = exp(estimate)
  ) %>% 
  select(term, OR = estimate, p.value)
 
nyc_airbnb %>% 
  modelr::add_predictions(logistic_fit) %>% 
  #get more readable probability values
  mutate(pred = boot::inv.logit(pred))
```




